\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classificaton for the Yelp Dataset Challenge}

### 2015-12-12 paper/article_2.tex

\begin{figure}[H]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    & OVI LDA & GS LDA & NMF \\ \hline
    Baseline: all False & 90,02 \% &  90.02 \% &  90.02 \% \\ \hline
    Kernel rbf SVM & 91.00\%  &  90.73\%  &  90.67\% \\ \hline
    Kernel rbf SVM + PCA & 90.62\%  &  90.85\%  &  90.85\% \\ \hline
    Logistic Regression & 91.39\%  &  91.86\%  &  91.86\%\\ \hline
    Logistic Regression + PCA & 92.37\%  &  92.89\%  &  93.16\% \\ \hline
    Lasso & 91.18\%  &  93.75\%  &  92.40\% \\ \hline
	Lasso + PCA & 92.53\%  &  94.83\%  &  93.35\% \\ \hline
    Random Forest & 92.12\% &  93.58\% &  93.37\% \\ \hline
    Random Forest + PCA & 92.84\% &  \textbf{94.66} \% &  94.06\% \\ \hline
    \end{tabular}
\end{center}
\caption{Classification results for different features}
\end{figure}

@@

\noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline. This confirms that the data is not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate. The logistic regression performs better under the l1 penalization because of the sparsity of our features. Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection the best estimator.\\

>>>>

\begin{figure}[H]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    & OVI LDA & GS LDA & NMF \\ \hline
    Baseline: all False & 90,02 \% &  90.02 \% &  90.02 \% \\ \hline
    Kernel rbf SVM & 91.00\%  &  90.73\%  &  90.67\% \\ \hline
    Kernel rbf SVM + PCA & 90.62\%  &  90.85\%  &  90.85\% \\ \hline
    Logistic Regression & 91.39\%  &  91.86\%  &  91.86\%\\ \hline
    Logistic Regression + PCA & 92.37\%  &  92.89\%  &  93.16\% \\ \hline
    Lasso & 91.18\%  &  93.75\%  &  92.40\% \\ \hline
	Lasso + PCA & 92.53\%  &  \textbf{94.83}\%  &  93.35\% \\ \hline
    Random Forest & 92.12\% &  93.58\% &  93.37\% \\ \hline
    Random Forest + PCA & 92.84\% &  94.66 \% &  94.06\% \\ \hline
    \end{tabular}
\end{center}
\caption{Classification results for different features}
\end{figure}

@@

\noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline. This confirms that the data is not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate. The logistic regression performs better under the l1 penalization because of the sparsity of our features. Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\
